\section{The Martini Lab}
\subsection{Background}
This is an example flask server (focused on UI-friendly, front-end design) to teach any new bartender how to make certain types of martinis. In order to help our users learn as fast and as efficiently as possible, the project includes 3 parts:
\begin{itemize}
    \item \textbf{Learning Portion}: This is an interactive learning feature that will help the users learn the recipes for the drinks as well as the necessary order to put ingredients in / be a true bartender. In this case, we have the user interact with our live-simulation bartending environment, which they will use to mimic the demands of a real  bar!
    \item \textbf{Written Quiz Portion:} This is a quiz that will test the user's knowledge on the drinks they have learned. It tests recipes, drink facts, and other things that would be useful for a bartender to know!
    \item \textbf{Bartending Simulator:} The final section is a bartending simulator that will test the user's ability to make drinks in a timely manner. This is a fun way to test the user's knowledge and see how they would do in a real bar setting.
\end{itemize}
Special shoutout to Nguyen Tran (who I love from the very depths of my heart) for helping me with the design of this project. Truly, a god among men.
\subsection{Resources}
\begin{itemize}
    \item \textbf{Demonstration Video:} \href{https://youtube.com/watch?v=3N8m4HOGbX0&ab_channel=ConnorSeanLi}{here}
    \item \textbf{GitHub Repo:} \href{https://github.com/connorli18/uiux-final-group4}{here}
\end{itemize}